PrepCAISOData

### 2014-12-17 CAData/CAISO/LoadData.Rmd
Getting ready to add trends data.

summary(lm(Actual~Forecast*Hour,data=Current))
summary(lm(Actual~Forecast*Hour,data=Lag))

@@

>>>>

summary(lm(Actual~Forecast,data=Current))
summary(lm(Actual~Forecast,data=Lag))

@@

```{r}
GoodDays<-names(table(CAISOWorking$OPR_DT)  )[table(CAISOWorking$OPR_DT)==48]
RevisedWorking<-CAISOWorking[is.element(CAISOWorking$OPR_DT,GoodDays),]
table(table(RevisedWorking$OPR_DT))

Forecast<-RevisedWorking[RevisedWorking$MARKET_RUN_ID=="7DA",]
Actual<-RevisedWorking[RevisedWorking$MARKET_RUN_ID=="ACTUAL",]

Current<-sqldf("select Actual.Hour, Actual.Date, Actual.MW as Actual, Forecast.MW as Forecast from Forecast, Actual where Actual.Hour=Forecast.Hour and Actual.Date=Forecast.Date;")
save(Current,file="Current.Rdata")
```

Now get the google trends data in and attached.
